Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices

### 2023-04-27 manuscript/manuscript.tex
Fixed requested Edits

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec: intro}
\jy{don't put space in labels}
%\paragraph{Overview of topic}

@@

\jy{refer to sections by their labels}

This following is a roadmap for this study: 1) Describing the Data, 2) Explaining the Statistical Methods and the Machine Learning Concepts, 3) Explaining the Results of our Paper, 4) Conducting Discussion of this Study.

@@

\section{Data Description} \jy{put section labels within the sections}
\label{sec: datadesc}

\jy{Merge those paragraphs that are overally small.}

For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool. Figure ~\ref{fig:stockdata} shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.

%%\jy{the figure x-labels are cutoff}
%%% fixed this
\begin{figure}[tbp]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig1.pdf}
  \caption{A plot of historic CVX stock data from 2021 to 2022.}\label{fig:stockdata}
  \end{center}
\end{figure}

While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: methods}
\section{Methods}

@@

\begin{figure}[tbp]
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
%Rounded Rect [id:dp4434986972980839] 
\draw   (100,43.8) .. controls (100,32.76) and (108.95,23.8) .. (120,23.8) -- (261,23.8) .. controls (272.05,23.8) and (281,32.76) .. (281,43.8) -- (281,103.8) .. controls (281,114.85) and (272.05,123.8) .. (261,123.8) -- (120,123.8) .. controls (108.95,123.8) and (100,114.85) .. (100,103.8) -- cycle ;
%Rounded Rect [id:dp8739677930569794] 
\draw   (359,68.2) .. controls (359,52.52) and (371.72,39.8) .. (387.4,39.8) -- (472.6,39.8) .. controls (488.28,39.8) and (501,52.52) .. (501,68.2) -- (501,168.4) .. controls (501,184.09) and (488.28,196.8) .. (472.6,196.8) -- (387.4,196.8) .. controls (371.72,196.8) and (359,184.09) .. (359,168.4) -- cycle ;
%Curve Lines [id:da9359490056283244] 
\draw    (282,73) .. controls (362,56.8) and (275,143.8) .. (359,124.8) ;
%Straight Lines [id:da03881732608220867] 
\draw    (78,72.8) -- (101,73) ;
%Straight Lines [id:da6091063106538472] 
\draw    (500,120.8) -- (523,121) ;
%Straight Lines [id:da19347919375178857] 
\draw    (431,215.8) -- (431,199.8) ;
% Text Node
\draw (161,65) node [anchor=north west][inner sep=0.75pt]   [align=left] {Encoder};
% Text Node
\draw (398,103) node [anchor=north west][inner sep=0.75pt]   [align=left] {Decoder};
% Text Node
\draw (42,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {Input};
% Text Node
\draw (524,112) node [anchor=north west][inner sep=0.75pt]   [align=left] {Output};
% Text Node
\draw (408,219) node [anchor=north west][inner sep=0.75pt]   [align=left] { Output Probabilites};
\end{tikzpicture}
\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder. \citep{devlin2018bert}.}
\label{fig:transformer}
\end{figure}
The Transformer architecture consists of two main components: an encoder and a decoder.The encoder takes in the input sequence and generates a sequence of hidden representations, which are then passed to the decoder. The decoder then uses the encoder's output to generate the final output sequence.

@@

\jy{put negative signs in math mode}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: results}
\section{Results}

@@

\jy{make the label of the vertical axis more informative}
\begin{figure}[tbp]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig4.pdf}
  \caption{Garch model residuals.}\label{fig:garchvar}
  \end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: discussion}
\section{Discussion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%\jy{don't put space in labels}
%\paragraph{Overview of topic}

@@

%%%\jy{refer to sections by their labels}
%%completed

This following is a roadmap for this study: Section \ref{sec:intro}: Introducing Concepts and Providing Background, Section \ref{sec:datadesc}: Describing the Data , Section \ref{sec:methods}: Explaining the Statistical Methods and the Machine Learning Concepts, Section \ref{sec:results}: Explaining the Results of our Paper, and Section \ref{sec:discussion}: Conducting Discussion of this Study.

@@

\section{Data Description} 
\label{sec:datadesc}
%%\jy{put section labels within the sections}

%%\jy{Merge those paragraphs that are overally small.}

For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool. Figure ~\ref{fig:stockdata} shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}. 
While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the closing Price and the Returns which can be taken by taking the log difference of the closing Prices, refer to Figure~{fig:returns}.
%%\jy{the figure x-labels are cutoff}
%%% fixed this
\begin{figure}[tbp]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig1.pdf}
  \caption{A plot of historic CVX stock data from 2021 to 2022.}\label{fig:stockdata}
  \end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
\label{sec:methods}

@@

\begin{figure}[tbp]
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
%Rounded Rect [id:dp4434986972980839] 
\draw   (100,43.8) .. controls (100,32.76) and (108.95,23.8) .. (120,23.8) -- (261,23.8) .. controls (272.05,23.8) and (281,32.76) .. (281,43.8) -- (281,103.8) .. controls (281,114.85) and (272.05,123.8) .. (261,123.8) -- (120,123.8) .. controls (108.95,123.8) and (100,114.85) .. (100,103.8) -- cycle ;
%Rounded Rect [id:dp8739677930569794] 
\draw   (359,68.2) .. controls (359,52.52) and (371.72,39.8) .. (387.4,39.8) -- (472.6,39.8) .. controls (488.28,39.8) and (501,52.52) .. (501,68.2) -- (501,168.4) .. controls (501,184.09) and (488.28,196.8) .. (472.6,196.8) -- (387.4,196.8) .. controls (371.72,196.8) and (359,184.09) .. (359,168.4) -- cycle ;
%Curve Lines [id:da9359490056283244] 
\draw    (282,73) .. controls (362,56.8) and (275,143.8) .. (359,124.8) ;
%Straight Lines [id:da03881732608220867] 
\draw    (78,72.8) -- (101,73) ;
%Straight Lines [id:da6091063106538472] 
\draw    (500,120.8) -- (523,121) ;
%Straight Lines [id:da19347919375178857] 
\draw    (431,215.8) -- (431,199.8) ;
% Text Node
\draw (161,65) node [anchor=north west][inner sep=0.75pt]   [align=left] {Encoder};
% Text Node
\draw (398,103) node [anchor=north west][inner sep=0.75pt]   [align=left] {Decoder};
% Text Node
\draw (42,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {Input};
% Text Node
\draw (524,112) node [anchor=north west][inner sep=0.75pt]   [align=left] {Output};
% Text Node
\draw (408,219) node [anchor=north west][inner sep=0.75pt]   [align=left] { Output Probabilites};
\end{tikzpicture}
\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder. \citep{devlin2018bert}.}
\label{fig:transformer}
\end{figure}
The Transformer architecture consists of two main components: an encoder and a decoder.The encoder takes in the input sequence and generates a sequence of hidden representations, which are then passed to the decoder. The decoder then uses the encoder's output to generate the final output sequence. Figure~\ref{fig:transformer} is a simple layout of this architecture

@@

%%\jy{put negative signs in math mode}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

@@

%%\jy{make the label of the vertical axis more informative}
\begin{figure}[tbp]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig4.pdf}
  \caption{Garch model residuals.}\label{fig:garchvar}
  \end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:discussion}
